# original R file form Zenodo
---
title: "Quantitative analysis - sample 1"
output:
  html_document:
    df_print: paged
  pdf_document: default
  word_document: default
---

### All the R package below are not necessary
```{r}
library(ggplot2)
library(QuantPsyc)
library(readr)
library(tidyr)
library(forcats)
library(readxl)
library(psych)
library(interactions)
library(plyr)
library(tidyverse)
library(Hmisc)
library(factoextra)
library(olsrr)
library(Hmisc)
library(xtable)
library(psy)
library(Superpower)
library(car)
library(plyr)
library(FactoMineR)
library(lattice)
library(devtools)
library(rmarkdown)
library(questionr)
library(lm.beta)
library(knitr)
library(ggplot2)
library(gghalves)
library(htmltools)
library(margins)
library(lme4)
library(lmerTest)
library(lmtest)
library(openxlsx)
library(dplyr)
library(lavaan)
library(grmsem)
library(ltm)
library(hrbrthemes)
```

### LOAD THE DATA 
```{r}
Physical_Effort_Scale_Data_Fall_2022 <- dataset
```

# rename some variables
```{r}
pes <- Physical_Effort_Scale_Data_Fall_2022
pes <- rename.variable(pes, "Consent 1","consent_1")
pes <- rename.variable(pes, "Consent 2","consent_2")
pes <- rename.variable(pes, "Q60","PA_profile")
```

## Apply inclusion and exclusion criteria
```{r}
pes <- pes[2:919,]
pes <- subset(pes, Finished == "True")
pes <- subset(pes, consent_1 == "Yes" & consent_2 == "Yes")
pes <- subset(pes, UserLanguage == "EN")
pes <- subset(pes, Finished == "True")
pes <- subset(pes, consent_1 == "Yes" & consent_2 == "Yes")
```

## select the variable of interest of the descriptive statistics
```{r}
pes_clean <- pes %>% dplyr::select(contains(c("pes")), "Gender", "Faculty", "Program" , "Year Program", "First Semester", "PA_profile")
```

## REPLACE VALUES OF PES AND OF PA Profile
```{r}
pes_clean[pes_clean=="1 - I completely disagree"] <- "1"
pes_clean[pes_clean=="2 - I disagree"] <- "2"
pes_clean[pes_clean=="3 - I neither agree nor disagree"] <- "3"
pes_clean[pes_clean=="4 - I agree"] <- "4"
pes_clean[pes_clean=="5 - I completely agree"] <- "5"

pes_clean["PA_profile"][pes_clean["PA_profile"] == "Regular hard physical training for competition sports: running events, orienteering, skiing, swimming, soccer, or similar activities, several times per week."] <- "Vigorous PA"
  
pes_clean["PA_profile"][pes_clean["PA_profile"] == "Regular moderate physical activity and training: heavy gardening, running, swimming, fitness, tennis, badminton, or similar activities, for at least 2 to 3 hours by week."] <- "Moderate PA"
    
pes_clean["PA_profile"][pes_clean["PA_profile"] == "Sedentary: being almost completely inactive: reading, TV watching, movies, using computers or doing other sedentary activities during leisure time."] <- "Inactive"
    
pes_clean["PA_profile"][pes_clean["PA_profile"] == "Some light physical activity: riding a bicycle, walking with the family, gardening, table tennis, bowling, or similar activities, for at least 4 hours by week."] <- "Light PA"

table(pes_clean$PA_profile)
```

## Descriptive statistics
```{r}
table(pes_clean$Gender)
table(pes_clean$Faculty)
table(pes_clean$`Year Program`)
```

## FIRST STEP PCA ANALYSIS
### REMOVE ALL INCOMPLETE DATA ON PES
```{r}
pes_na <- na.omit(pes_clean)
```

# create the data set (pes_efa), with only the 8 items
```{r}
pes_efa <- pes_na %>% dplyr::select(contains("pes_"))
pes_efa <- pes_efa[,5:22]
```

```{r}
pes_efa <- pes_efa %>% mutate_if(is.character, as.numeric)
```

```{r}
dial.pca <- princomp(as.matrix(pes_efa))
summary(dial.pca)
```
```{r}
screeplot(dial.pca,npcs=15) #npcs is the number of components to plot, should be more than n dimensions expected
```
****************************************
Three criteria
(1)	The bend (number of factors before the elbow)
(2)	The component (based on the eigenvalues (i.e., standard deviation in the R output) based on the Kaiser’s rule of > 1. 
(3)	The >80% of variance explained (but usually not reached in social sciences).
In our case, (1) suggest 1 factor and (2) suggest 3 factors.
Thus, we have to test an EFA with one factor, with 3 factors, but also with 2 factors as theoretical expected.
****************************************

## SECOND STEP EFA ANALYSIS (promax rotation)
```{r}
dial.efa_1F <- factanal(as.matrix(pes_efa),factors=1,
                     cor=T,rotation="promax")
print(dial.efa_1F)
```

```{r}
dial.efa_2F <- factanal(as.matrix(pes_efa),factors=2,
                     cor=T,rotation="promax")
print(dial.efa_2F)
```

```{r}
dial.efa_3F <- factanal(as.matrix(pes_efa),factors=3,
                     cor=T,rotation="promax")
print(dial.efa_3F)
```

## THIRD STEP: ITEM RESPONSE THEORY
****************************************
one analysis for each dimension separately.

# APPROACH DIMENSION
```{r}
pes_efa_app <- pes_efa[,c(1,3,5,7,9,11,13,15,18)]
```

```{r}
dimension1.grm <- grm(pes_efa_app, Hessian = TRUE)
dimension1 <- descript(pes_efa_app,chi.squared=F)

plot(dimension1.grm, type = "IIC", lwd = 2, cex = 1, legend = TRUE, cx = "topright",main="",
     xlab = "Approach toward effort", cex.main = 1.2, cex.lab = 1.2, cex.axis = 1.1)
```

# response modalities
```{r}
table (pes_efa$PES_1)
table (pes_efa$PES_3)
table (pes_efa$PES_5)
table (pes_efa$PES_7)
table (pes_efa$PES_9)
table (pes_efa$PES_11)
table (pes_efa$PES_13)
table (pes_efa$PES_15)
table (pes_efa$PES_18)

```

```{r}
pes_efa_app_short <- pes_efa[,c(3,7,15,18)]
```

```{r}
dimension1.grm <- grm(pes_efa_app_short, Hessian = TRUE)
dimension1 <- descript(pes_efa_app_short,chi.squared=F)

plot(dimension1.grm, type = "IIC", lwd = 2, cex = 1, legend = TRUE, cx = "topright",main="",
     xlab = "Approach toward effort", cex.main = 1.2, cex.lab = 1.2, cex.axis = 1.1)
```
 
# AVOIDANCE DIMENSION
```{r}
pes_efa_avoid <- pes_efa[,c(2,4,6,8,10,12,14,16,17)]
```

```{r}
dimension1.grm <- grm(pes_efa_avoid, Hessian = TRUE)
dimension1 <- descript(pes_efa_avoid,chi.squared=F)

plot(dimension1.grm, type = "IIC", lwd = 2, cex = 1, legend = TRUE, cx = "topright",main="",
     xlab = "Avoidance toward effort", cex.main = 1.2, cex.lab = 1.2, cex.axis = 1.1)
```
# response modalities

```{r}
table (pes_efa$PES_2)
table (pes_efa$PES_4)
table (pes_efa$PES_6)
table (pes_efa$PES_8)
table (pes_efa$PES_10)
table (pes_efa$PES_12)
table (pes_efa$PES_14)
table (pes_efa$PES_16)
table (pes_efa$PES_17)
```

#Second analysis for the avoidance dimension wit less items (without 10 and 16)
```{r}
pes_efa_avoid_short <- pes_efa[,c(4,6,12,17)]
```

```{r}
dimension1.grm <- grm(pes_efa_avoid_short, Hessian = TRUE)
dimension1 <- descript(pes_efa_avoid_short,chi.squared=F)

plot(dimension1.grm, type = "IIC", lwd = 2, cex = 1, legend = TRUE, cx = "topright",main="",
     xlab = "Avoidance toward effort", cex.main = 1.2, cex.lab = 1.2, cex.axis = 1.1)
```

## STEP 3: CFA analysis
```{r}
pes_na <- pes_na %>% mutate_at(c("PES_1", "PES_3", "PES_5","PES_7", "PES_9", "PES_11", "PES_13", "PES_15", "PES_18", "PES_2", "PES_4", "PES_6","PES_8", "PES_10", "PES_12", "PES_14", "PES_16", "PES_17"), as.numeric)
```

```{r}
model_cfa1 <-'
approach =~ PES_3 + PES_7 + PES_18 + PES_15 
avoidance =~ PES_4 + PES_6 + PES_12 + PES_17

approach ~~ avoidance
'

fit<- lavaan::sem(model_cfa1,data=pes_na,orthogonal = TRUE)

summary(fit,fit.measures=TRUE,standardized=TRUE,rsquare=TRUE, ci = .95)
```
## INTERNAL CONSISTENCY ACROSS DIMENSIONS 
## FOR THE APPROACH DIMENSION
```{r}
pes_approach <- pes_efa %>% dplyr::select("PES_3","PES_7", "PES_15", "PES_18")
```

```{r}
cronbach(pes_approach)
```
## FOR THE AVOIDANCE DIMENSION
```{r}
pes_avoid <- pes_efa %>% dplyr::select("PES_4", "PES_6", "PES_12", "PES_17")
```

```{r}
cronbach(pes_avoid)
```

### PRELIMINARY CONSTRCUT VALIDITY: DESCRIBE BY PA PROFILE 
```{r}
library(gghalves)
library(hrbrthemes)
library(MetBrewer)
```

```{r}
pes_na <- mutate(pes_na, pes_approach = (PES_3 + PES_7 + PES_15 + PES_18)/4)

pes_na <- mutate(pes_na, pes_avoid = (PES_4 + PES_6 + PES_12 + PES_17)/4)
```


### Approach dimension
```{r, warning = FALSE}
ggplot(pes_na, aes(x = PA_profile, y = pes_approach, fill = PA_profile, color = PA_profile)) +
  geom_half_violin(position = position_nudge(x=0.1), 
                   side="r", 
                   alpha =.8, 
                   color = "white") + 
  
  geom_jitter(width = .05, 
              height = 0, 
              alpha = .1) +
  
  stat_summary(aes(group = PA_profile), 
               geom = "pointrange",fun = "mean", 
               fun.min = function(x) mean(x) - sd(x)/2, 
               fun.max = function(x) mean(x) + sd(x)/2, 
               size = .75, 
               alpha = 1) +
  
  scale_color_manual(values=met.brewer("Cross", 4)) +
  
  scale_fill_manual(values=met.brewer("Cross", 4)) +
  
  
  scale_y_continuous(limits = c(1,5), breaks = c(1, 2, 3, 4, 5)) + 
  
  ylab("Approach dimension") +

  xlab("PA profile") +
  theme_classic() + guides(fill="none", color = "none") 
```

## FOR THE AVOIDANCE DIMENSION 
```{r}
ggplot(pes_na, aes(x = PA_profile, y = pes_avoid, fill = PA_profile, color = PA_profile)) +
  geom_half_violin(position = position_nudge(x=0.1), 
                   side="r", 
                   alpha =.8, 
                   color = "white") + 
  
  geom_jitter(width = .05, 
              height = 0, 
              alpha = .1) +
  
  stat_summary(aes(group = PA_profile), 
               geom = "pointrange",fun = "mean", 
               fun.min = function(x) mean(x) - sd(x)/2, 
               fun.max = function(x) mean(x) + sd(x)/2, 
               size = .75, 
               alpha = 1) +
  
  scale_color_manual(values=met.brewer("Cross", 4)) +
  
  scale_fill_manual(values=met.brewer("Cross", 4)) +
  
  
  scale_y_continuous(limits = c(1,5), breaks = c(1, 2, 3, 4, 5)) + 
  
  ylab("Avoid dimension") +

  xlab("PA profile") +
  theme_classic() + guides(fill="none", color = "none") 
```
# multiple linear regression
```{r}
RLM_approach <- lm(pes_approach ~ PA_profile, data = pes_na)
summary(RLM_approach)
```


